---
title: "Myanmanr Census - Age distribution of farming population"
tables: yes
output:
  html_document:
    css: custom.css
    toc: yes
  word_document:
    toc: yes
---
    
```{r setup, echo = FALSE, warning = FALSE, message = FALSE}
  ###############################################################################
  ## First look at census data - unique generations
  ###############################################################################
  
  
  ## Preliminaries
  ###############################################################################
  library(knitr)
  library(tidyverse)
  library(memisc)
  library(RColorBrewer)
  library(xtable)
  kh01 <- as.data.frame(as.data.set(spss.system.file("../outputs/KH01.sav")))
  
  options(scipen = 9999, digits = 6)
```
  

## "Farming Population"

I've put "farming population" in quotes, because the data I have refers to households and/or heads of households, not all of the individuals. 

Furthermore I have three different definitions of what a farming household might be. So here are the data for all three definitions looking at age distribution only.

**FYI I also have this for regions, as well as Head of HH disability (number of) and head of HH gender.**

### Farming HH 1: Head is skilled farmer

```{r, echo = FALSE}
kh01.01 <- kh01 %>%
  filter(tablenumber_ == 1, var1 != "Total") %>%
  dplyr::select(-tablenumber_, -total, -command_, -subtype_, -var4, -var6, -label_) %>%
  dplyr::rename(region = var1, hh_type = var2, sex = var3, disability = var5) %>% 
  gather(key = age.group, value = count, 5:22 ) %>% 
  separate(age.group, c("A", "age.group")) %>% 
  dplyr::select(-A) %>% 
  filter(disability != "") %>% 
  filter(region != "Total",
         hh_type != "Total",
         sex != "Total",
         disability != "Total") %>% 
  dplyr::select(age.group, region, sex, disability, hh_type, count) %>% 
  arrange(age.group, region, sex, disability, hh_type) %>% 
  mutate(hh_type = ifelse(hh_type == "not farming", 0, 1)) %>% 
  group_by(age.group, region, sex, disability, hh_type) %>% 
  dplyr::summarise(count = sum(count, na.rm = TRUE)) %>% 
  ungroup() 
  

kh01.01 %>% 
  group_by(age.group, hh_type) %>% 
  dplyr::summarise(count = sum(count, na.rm = TRUE)) %>%  ungroup() %>% 
  mutate(age.group = as.character(age.group)) %>% 
  separate(age.group, 2, into = c("from", "to")) %>% 
  unite(age.group, from, to, sep = "-") %>% 
  mutate(age.group = ifelse(age.group == "14-", "-14", age.group))-> age.dist


age.dist %>% spread(hh_type, count, sep="_") %>% 
  dplyr::rename(non.farm = hh_type_0, 
                farm = hh_type_1) %>% 
  mutate(non.farm.percent = non.farm/sum(non.farm)*100,
         farm.percent = farm/sum(farm)*100) -> age.dist.table
```
So in the first type of "farming households" these are households where:

 1. The head of the HH is in a farming occupation (ISCO classification category 6: Skilled Agricultural, Forestry and Fishery Workers), AND
 2. The head of the HH is not an employee. (Their Activity status is either Employer or Contributing family worker) 

There are `r sum(age.dist.table$farm)` such households out of `r sum(age.dist.table$non.farm, age.dist.table$farm)`, so `r 100*sum(age.dist.table$farm)/sum(age.dist.table$non.farm, age.dist.table$farm)` %.

Then we can look at the age distribution of the *heads of these households*.  

```{r results='asis', echo=FALSE, fig.height=6, fig.cap = "Figure 1: Age distribution of heads of households that are in skilled farming occupation or not - counts"}


par(xpd = TRUE, mar = c(3,7,1,1))
yz <- barplot(t(as.matrix(age.dist.table[2:3])), beside = TRUE, col = c("indianred2", "darkslategray2"), horiz = TRUE, legend.text = c("not farmers", "farmers"))
text(-60000,colMeans(yz), age.dist.table[[1]], las = 2)

```



```{r results='asis', echo=FALSE, fig.height=6, fig.cap = "Figure 2: Age distribution of heads of households that are in skilled farming occupation or not - percentages"}
par(xpd = TRUE, mar = c(3,7,1,1))

yz <- barplot(t(as.matrix(age.dist.table[4:5])), beside = TRUE, col = c("indianred2", "darkslategray2"), horiz = TRUE, legend.text = c("not farmers", "farmers"))
text(-0.7,colMeans(yz), age.dist.table[[1]], las = 2)

```

Table 1: Age distribution of heads of households of type 1 farming (and non farming)
```{r results='asis', echo=FALSE}
kable(age.dist.table, digits = 2, booktabs = TRUE, padding = 10)
```


### Farming HH 2: Head or spouse is skilled farmer
```{r, echo = FALSE} 
 kh01.01 <- kh01 %>%
  filter(tablenumber_ == 2, var1 != "Total") %>%
  dplyr::select(-tablenumber_, -total, -command_, -subtype_, -var4, -var6, -label_) %>%
  dplyr::rename(region = var1, hh_type = var2, sex = var3, disability = var5) %>% 
  gather(key = age.group, value = count, 5:22 ) %>% 
  separate(age.group, c("A", "age.group")) %>% 
  dplyr::select(-A) %>% 
  filter(disability != "") %>% 
  filter(region != "Total",
         hh_type != "Total",
         sex != "Total",
         disability != "Total") %>% 
  dplyr::select(age.group, region, sex, disability, hh_type, count) %>% 
  arrange(age.group, region, sex, disability, hh_type) %>% 
  mutate(hh_type = ifelse(hh_type == "not farming", 0, 1)) %>% 
  group_by(age.group, region, sex, disability, hh_type) %>% 
  dplyr::summarise(count = sum(count, na.rm = TRUE)) %>% 
  ungroup() 
  

kh01.01 %>% 
  group_by(age.group, hh_type) %>% 
  dplyr::summarise(count = sum(count, na.rm = TRUE)) %>%  ungroup() %>% 
  mutate(age.group = as.character(age.group)) %>% 
  separate(age.group, 2, into = c("from", "to")) %>% 
  unite(age.group, from, to, sep = "-") %>% 
  mutate(age.group = ifelse(age.group == "14-", "-14", age.group))-> age.dist


age.dist %>% spread(hh_type, count, sep="_") %>% 
  dplyr::rename(non.farm = hh_type_0, 
                farm = hh_type_1) %>% 
  mutate(non.farm.percent = non.farm/sum(non.farm)*100,
         farm.percent = farm/sum(farm)*100) -> age.dist.table

```
In the second  type of "farming households" these are households where:

 1. The head or the spouse of the head of the HH is in a farming occupation (ISCO classification category 6: Skilled Agricultural, Forestry and Fishery Workers), AND
 2. That person is not an employee. (Their Activity status is either Employer or Contributing family worker) 

There are `r sum(age.dist.table$farm)` such households out of `r sum(age.dist.table$non.farm, age.dist.table$farm)`, so `r 100*sum(age.dist.table$farm)/sum(age.dist.table$non.farm, age.dist.table$farm)` %.

Then we can look at the age distribution of the *heads of these households* - Important!! SO again: this is the age distribution of the heads of household, who may not be farmers, but in that case their spouse is!  

```{r results='asis', echo=FALSE, fig.height=6, fig.cap = "Figure 3: Age distribution of heads of households who  are (or their spouses) in skilled farming occupation or not - counts"}

par(xpd = TRUE, mar = c(3,7,1,1))
yz <- barplot(t(as.matrix(age.dist.table[2:3])), beside = TRUE, col = c("indianred2", "darkslategray2"), horiz = TRUE, legend.text = c("not farmers", "farmers"))
text(-60000,colMeans(yz), age.dist.table[[1]], las = 2)

```



```{r results='asis', echo=FALSE, fig.height=6, fig.cap = "Figure 4: Age distribution of heads of households who  are (or their spouses) in skilled farming occupation or not - percentages"}
par(xpd = TRUE, mar = c(3,7,1,1))

yz <- barplot(t(as.matrix(age.dist.table[4:5])), beside = TRUE, col = c("indianred2", "darkslategray2"), horiz = TRUE, legend.text = c("not farmers", "farmers"))
text(-0.7,colMeans(yz), age.dist.table[[1]], las = 2)

```

Table 2: Age distribution of heads of households of type 2 farming (and non farming)
```{r results='asis', echo=FALSE}
kable(age.dist.table, digits = 2, booktabs = TRUE, padding = 10)
```

### Farming HH 3: Any relative in HH is skilled farmer
```{r, echo = FALSE}
kh01.01 <- kh01 %>%
  filter(tablenumber_ == 3, var1 != "Total") %>%
  dplyr::select(-tablenumber_, -total, -command_, -subtype_, -var4, -var6, -label_) %>%
  dplyr::rename(region = var1, hh_type = var2, sex = var3, disability = var5) %>% 
  gather(key = age.group, value = count, 5:22 ) %>% 
  separate(age.group, c("A", "age.group")) %>% 
  dplyr::select(-A) %>% 
  filter(disability != "") %>% 
  filter(region != "Total",
         hh_type != "Total",
         sex != "Total",
         disability != "Total") %>% 
  dplyr::select(age.group, region, sex, disability, hh_type, count) %>% 
  arrange(age.group, region, sex, disability, hh_type) %>% 
  mutate(hh_type = ifelse(hh_type == "not farming", 0, 1)) %>% 
  group_by(age.group, region, sex, disability, hh_type) %>% 
  dplyr::summarise(count = sum(count, na.rm = TRUE)) %>% 
  ungroup() 
  

kh01.01 %>% 
  group_by(age.group, hh_type) %>% 
  dplyr::summarise(count = sum(count, na.rm = TRUE)) %>%  ungroup() %>% 
  mutate(age.group = as.character(age.group)) %>% 
  separate(age.group, 2, into = c("from", "to")) %>% 
  unite(age.group, from, to, sep = "-") %>% 
  mutate(age.group = ifelse(age.group == "14-", "-14", age.group))-> age.dist


age.dist %>% spread(hh_type, count, sep="_") %>% 
  dplyr::rename(non.farm = hh_type_0, 
                farm = hh_type_1) %>% 
  mutate(non.farm.percent = non.farm/sum(non.farm)*100,
         farm.percent = farm/sum(farm)*100) -> age.dist.table
```
In the third type of "farming households" these are households where:

 1. Any relative in the HH is in a farming occupation (ISCO classification category 6: Skilled Agricultural, Forestry and Fishery Workers), AND
 2. That person is not an employee. (Their Activity status is either Employer or Contributing family worker) 
 
There are `r sum(age.dist.table$farm)` such households out of `r sum(age.dist.table$non.farm, age.dist.table$farm)`, so `r 100*sum(age.dist.table$farm)/sum(age.dist.table$non.farm, age.dist.table$farm)` %.
 
Then we can look at the age distribution of the *heads of these households* - Important!! SO again: this is the age distribution of the heads of household, who may not be farmers - but someone related to them in the HH is!  

```{r results='asis', echo=FALSE, fig.height=6, fig.cap = "Figure 5: Age distribution of heads of households where  at least one relative is in a skilled farming occupation or not - counts"}

par(xpd = TRUE, mar = c(3,7,1,1))
yz <- barplot(t(as.matrix(age.dist.table[2:3])), beside = TRUE, col = c("indianred2", "darkslategray2"), horiz = TRUE, legend.text = c("not farmers", "farmers"))
text(-60000,colMeans(yz), age.dist.table[[1]], las = 2)

```



```{r results='asis', echo=FALSE, fig.height=6, fig.cap = "Figure 6: Age distribution of heads of households where  at least one relative is in a skilled farming occupation or not - percentages"}
par(xpd = TRUE, mar = c(3,7,1,1))

yz <- barplot(t(as.matrix(age.dist.table[4:5])), beside = TRUE, col = c("indianred2", "darkslategray2"), horiz = TRUE, legend.text = c("not farmers", "farmers"))
text(-0.7,colMeans(yz), age.dist.table[[1]], las = 2)

```

Table 3: Age distribution of heads of households of type 3 farming (and non farming)
```{r results='asis', echo=FALSE}
kable(age.dist.table, digits = 2, booktabs = TRUE, padding = 10)
```

