---
title: "Ken - extra queries 18.3.17"
tables: yes
output:
  html_document:
    css: custom.css
    toc: yes
---

```{r setup, echo = FALSE, warning = FALSE, message = FALSE}
library(knitr)
library(dplyr)
library(vcd)
load("../data/survey.data03.RData")
source("R04-MyFunctions.R")
```


### Household size by region only

Boxplot standards are:

* median (not mean) as the darkest line
* 25 and 75 percentiles are the top and bottom of the boxes
* The whiskers are meant to be the range of non outliers (1.5 times the interquartile range - the height of the box)
* and then teh outliers as points beyond that

#### `r description(I(dataset$q7))` 
```{r results='asis', echo=FALSE, fig.height=5}
var <- "q7"
Fun04PrintTabInt.region(var)
Fun04BarplotInt.region(var)
              
```


### Household income by region only

Like I said before, we only have an income category, and with the top category over 300,000 being open ended - and so large in the delta, there is no way to reasonably estimate an average value.  

#### `r description(I(dataset$q12))` 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q12
Fun04PrintTab.region(var)
Fun04Barplot.region(var)
```


## HH managing style

*Re query 16.3.: *

"Nearly all HHs in the dry sample have children who are involved in different ways in the work of the farm – either as sole managers or as co-managers or as a source of regular labour”.  Could you tell me %? And then same for sons or sons-in-law?"

* Partial answer here, based on managing stype only, not source of regular labour. Mainly because "source of regular labour" is very poorly defined.. Because we have 5 types of tasks and up to 5 hh members helping with each. For whatever number of days. So that's essentially a 5 x 5 table, so I'm not sure how to extract a "source of regular labour"  definition out of it, but see bellow


### Type of co-manageing style by Region, by age, and by holding size

#### `r description(I(dataset$n182))` 
[N = `r sum(!is.na(data$n182))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- dataset$n182
Fun02PrintTab(var)
Fun02Barplot(var)
```

### Type of co-manageing style by region AND age group 

#### `r description(I(dataset$n182))` 
[N = `r sum(!is.na(data$n182))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- dataset$n182
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```



## HH labour sources

*Re query 17.3.: *

"I want some idea not just of person-days that HH members were employed on farm work, but also numbers (of HH members).  "

" EG Are there any HHs where no-one other than the respondent works on the land (i.e. helps with any of the tasks we listed)?  "

"( then also it would be good to know frequencies/percentages for : respondent + 1 other ; respondent +  2 others...etc)"


### Number of HH members helping by Region, by age, and by holding size

#### `r description(I(dataset$n183))`

[N = `r sum(!is.na(data$n183))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- "n183"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```

### Number of HH members helping by Region ANDage

#### `r description(I(dataset$n183))`
```{r results='asis', echo=FALSE, fig.height=6}
var <- "n183"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```


### Number of person days of Household farm labour by Region, by age, and by holding size

#### `r description(I(dataset$n185))`

[N = `r sum(!is.na(data$n185))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- "n185"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```

### Number of person days of Household farm labour by Region AND age

#### `r description(I(dataset$n185))`
```{r results='asis', echo=FALSE, fig.height=6}
var <- "n185"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```


### Average number of days per Household farm labourer, by Region, by age, and by holding size

#### `r description(I(dataset$n186))`

[N = `r sum(!is.na(data$n186))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- "n186"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```

### Average number of days per Household farm labourer, by Region AND age

#### `r description(I(dataset$n186))`
```{r results='asis', echo=FALSE, fig.height=6}
var <- "n186"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```

## HH labour pattern

### Number of members and/or HoH farming contribution, by Region, by age, and by holding size

#### `r description(I(dataset$n187))`

[N = `r sum(!is.na(data$n187))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- dataset$n187
Fun02PrintTab(var)
Fun02Barplot(var) 
```

### Number of members and/or HoH farming contribution,  by Region AND age

#### `r description(I(dataset$n187))`
```{r results='asis', echo=FALSE, fig.height=6}
var <- dataset$n187
Fun03PrintTab(var)[[1]]
Fun03Barplot(var) 
```

## Hired labour pattern

Based on KH: 17.3.17: 

"Similar question for hired labour: are there any HHs which rely entirely oh HH labour? (i.e. no-one hired to help with any tasks)?  

### Ratio of Household to Hired Labour by Region, by age, and by holding size

#### `r description(I(dataset$n188))`
```{r results='asis', echo=FALSE, fig.height=6}
var <- "n188"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```

### Ratio of Household to Hired Labour by Region AND by age

#### `r description(I(dataset$n188))`
```{r results='asis', echo=FALSE, fig.height=6}
var <- "n188"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```



### Almost all labour HH/hired  by Region, by age, and by holding size

Because only a tiny number (like four or sth) have exclusively HH labour, and slightly more exclusively hired labour I used 5 \% as the "almost" level.  
 
#### `r description(I(dataset$n189))`

[N = `r sum(!is.na(data$n189))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- dataset$n189
Fun02PrintTab(var)
Fun02Barplot(var) 
```

### Almost all labour HH/hired  by Region AND age

#### `r description(I(dataset$n189))`
```{r results='asis', echo=FALSE, fig.height=6}
var <- dataset$n189
Fun03PrintTab(var)[[1]]
Fun03Barplot(var) 
```
