---
title: "Likert scales on technology and mechainisation"
author: "mz"
date: "21.2.2017"
output:
  pdf_document:
    number_sections: yes
    toc: yes
    toc_depth: 3
  word_document:
    reference_docx: StyleReference.docx
    toc: yes
    toc_depth: '3'
html_document: default
word_document html_document: default
---


```{r setup, echo = FALSE, warning = FALSE, message = FALSE}
library(dplyr)
library(lattice)
require(grid)
require(latticeExtra)
require(HH)

load("../data/survey.dataframe.RData")
# n151 - older than 60
data %>% mutate(n151 = factor(ifelse(q2<60, 0, 1), labels = c("Under 60", "Over 60"))) ->  data
levels(data$n151) <- c("Under 60", "Over 60")
```

# Question 57: the effects of the use of agricultural machinery 

## Likert scale for all four subquestions (N=600)


```{r, echo = FALSE}
sgbar.likert <- prop.table(table(data$q57a))*100
sgbar.likert<- rbind(sgbar.likert, prop.table(table(data$q57b))*100)
sgbar.likert<- rbind(sgbar.likert, prop.table(table(data$q57c))*100)
sgbar.likert<- rbind(sgbar.likert, prop.table(table(data$q57d))*100)

rownames(sgbar.likert) <- c("Higher yield", "Ease of farming", "Soil quality", "Crop quality")


likert(as.matrix(sgbar.likert),
       main=list(label="Do you think using agricultural machinery can lead to:", cex=0.75),
       xlab= list("Percentage", cex = 0.75))

```

## Under/over age 60 on Q57

### Under/over age 60 on Q57.a (higher yields)

```{r, echo = FALSE, fig.height = 3.5}
sgbar.likert <- prop.table(table(data$n151,data$q57a),1)*100

likert(sgbar.likert,
       main=list(label="Do you think using agricultural machinery can lead to higher yields", cex=0.75),
       xlab= list("Percentage", cex = 0.75),
       cex.main = 2)
```

### Under/over age 60 on Q57.b (ease of farming)
```{r, echo = FALSE, fig.height = 3.5}
sgbar.likert <- prop.table(table(data$n151,data$q57b),1)*100

likert(sgbar.likert,
       main=list(label="Do you think using agricultural machinery can lead to incresed ease of farming", cex=0.75),
       xlab= list("Percentage", cex = 0.75),
       cex.main = 2)
```

### Under/over age 60 on Q57.c (soil quality)
```{r, echo = FALSE, fig.height = 3.5}
sgbar.likert <- prop.table(table(data$n151,data$q57c),1)*100

likert(sgbar.likert,
       main=list(label="Do you think using agricultural machinery can lead to incresed soil quality", cex=0.75),
       xlab= list("Percentage", cex = 0.75),
       cex.main = 2)
```

### Under/over age 60 on Q57.d (crop quality)
```{r, echo = FALSE, fig.height = 3.5}
sgbar.likert <- prop.table(table(data$n151,data$q57d),1)*100

likert(sgbar.likert,
       main=list(label="Do you think using agricultural machinery can lead to incresed crop quality", cex=0.75),
       xlab= list("Percentage", cex = 0.75),
       cex.main = 2)
```


## Regional variation on Q57

### Regional variation on Q57.a (higher yields)

```{r, echo = FALSE, fig.height = 3.5}
sgbar.likert <- prop.table(table(data$id1,data$q57a),1)*100

likert(sgbar.likert,
       main=list(label="Do you think using agricultural machinery can lead to higher yields", cex=0.75),
       xlab= list("Percentage", cex = 0.75),
       cex.main = 2)
```

### Regional variation on Q57.b (ease of farming)
```{r, echo = FALSE, fig.height = 3.5}
sgbar.likert <- prop.table(table(data$id1,data$q57b),1)*100

likert(sgbar.likert,
       main=list(label="Do you think using agricultural machinery can lead to incresed ease of farming", cex=0.75),
       xlab= list("Percentage", cex = 0.75),
       cex.main = 2)
```

### Regional variation on Q57.c (soil quality)

```{r, echo = FALSE, fig.height = 3.5}
sgbar.likert <- prop.table(table(data$id1,data$q57c),1)*100

likert(sgbar.likert,
       main=list(label="Do you think using agricultural machinery can lead to incresed soil quality", cex=0.75),
       xlab= list("Percentage", cex = 0.75),
       cex.main = 2)
```

### Regional variation on Q57.d (crop quality)
```{r, echo = FALSE, fig.height = 3.5}
sgbar.likert <- prop.table(table(data$id1,data$q57d),1)*100

likert(sgbar.likert,
       main=list(label="Do you think using agricultural machinery can lead to incresed crop quality", cex=0.75),
       xlab= list("Percentage", cex = 0.75),
       cex.main = 2)
```



# Question 59: the limits on purcgasing of agricultural machinery 

## Likert scale for all five subquestions (N=600)


```{r, echo = FALSE}
sgbar.likert <- prop.table(table(data$q59a))*100
sgbar.likert<- rbind(sgbar.likert, prop.table(table(data$q59b))*100)
sgbar.likert<- rbind(sgbar.likert, prop.table(table(data$q59c))*100)
sgbar.likert<- rbind(sgbar.likert, prop.table(table(data$q59d))*100)
sgbar.likert<- rbind(sgbar.likert, prop.table(table(data$q59e))*100)
rownames(sgbar.likert) <- c("Insuff. knowledge/info", "No enough money", "Limited access to credit", "Fear of failure", "Field characteristics")


likert(as.matrix(sgbar.likert),
       main=list(label="Do you think your ability to purchase agricultural machinery is limited by:", cex=0.75),
       xlab= list("Percentage", cex = 0.75))

```

## Under/over age 60 on Q59

### Under/over age 60 on Q59.a (not enough knowledge/information)

```{r, echo = FALSE, fig.height = 3.5}
sgbar.likert <- prop.table(table(data$n151,data$q59a),1)*100

likert(sgbar.likert,
       main=list(label="Do you think your ability to purchase agricultural machinery is limited by insufficient knowledge", cex=0.75),
       xlab= list("Percentage", cex = 0.75),
       cex.main = 2)
```

### Under/over age 60 on Q59.b (not enough money)

```{r, echo = FALSE, fig.height = 3.5}
sgbar.likert <- prop.table(table(data$n151,data$q59b),1)*100

likert(sgbar.likert,
       main=list(label="Do you think your ability to purchase agricultural machinery is limited by not enough money", cex=0.75),
       xlab= list("Percentage", cex = 0.75),
       cex.main = 2)
```

### Under/over age 60 on Q59.c (limited access to credit)

```{r, echo = FALSE, fig.height = 3.5}
sgbar.likert <- prop.table(table(data$n151,data$q59c),1)*100

likert(sgbar.likert,
       main=list(label="Do you think your ability to purchase agricultural machinery is limited by limited access to credit", cex=0.75),
       xlab= list("Percentage", cex = 0.75),
       cex.main = 2)
```

### Under/over age 60 on Q59.d (fear of failure)

```{r, echo = FALSE, fig.height = 3.5}
sgbar.likert <- prop.table(table(data$n151,data$q59d),1)*100

likert(sgbar.likert,
       main=list(label="Do you think your ability to purchase agricultural machinery is limited by fear of failure", cex=0.75),
       xlab= list("Percentage", cex = 0.75),
       cex.main = 2)
```

### Under/over age 60 on Q59.e (field characteristics)

```{r, echo = FALSE, fig.height = 3.5}
sgbar.likert <- prop.table(table(data$n151,data$q59e),1)*100

likert(sgbar.likert,
       main=list(label="Do you think your ability to purchase agricultural machinery is limited by field characteristics", cex=0.75),
       xlab= list("Percentage", cex = 0.75),
       cex.main = 2)
```

## Regional variation on Q59

### Regional variation0 on Q59.a (not enough knowledge/information)

```{r, echo = FALSE, fig.height = 3.5}
sgbar.likert <- prop.table(table(data$id1,data$q59a),1)*100

likert(sgbar.likert,
       main=list(label="Do you think your ability to purchase agricultural machinery is limited by insufficient knowledge", cex=0.75),
       xlab= list("Percentage", cex = 0.75),
       cex.main = 2)
```

### Regional variation on Q59.b (not enough money)

```{r, echo = FALSE, fig.height = 3.5}
sgbar.likert <- prop.table(table(data$id1,data$q59b),1)*100

likert(sgbar.likert,
       main=list(label="Do you think your ability to purchase agricultural machinery is limited by not enough money", cex=0.75),
       xlab= list("Percentage", cex = 0.75),
       cex.main = 2)
```

### Regional variation on Q59.c (limited access to credit)

```{r, echo = FALSE, fig.height = 3.5}
sgbar.likert <- prop.table(table(data$id1,data$q59c),1)*100

likert(sgbar.likert,
       main=list(label="Do you think your ability to purchase agricultural machinery is limited by limited access to credit", cex=0.75),
       xlab= list("Percentage", cex = 0.75),
       cex.main = 2)
```

### Regional variation on Q59.d (fear of failure)

```{r, echo = FALSE, fig.height = 3.5}
sgbar.likert <- prop.table(table(data$id1,data$q59d),1)*100

likert(sgbar.likert,
       main=list(label="Do you think your ability to purchase agricultural machinery is limited by fear of failure", cex=0.75),
       xlab= list("Percentage", cex = 0.75),
       cex.main = 2)
```

### Regional variation on Q59.e (field characteristics)

```{r, echo = FALSE, fig.height = 3.5}
sgbar.likert <- prop.table(table(data$id1,data$q59e),1)*100

likert(sgbar.likert,
       main=list(label="Do you think your ability to purchase agricultural machinery is limited by field characteristics", cex=0.75),
       xlab= list("Percentage", cex = 0.75),
       cex.main = 2)
```

# Question 61: social norm/pressure on ownership of machinery

## Likert scale for all two subquestions (N=600)


```{r, echo = FALSE}
sgbar.likert <- prop.table(table(data$q61a))*100
sgbar.likert<- rbind(sgbar.likert, prop.table(table(data$q61b))*100)
rownames(sgbar.likert) <- c("Neighbouring farmers", "Household members")


likert(as.matrix(sgbar.likert),
       main=list(label="How much is your ownership of machinery appreciated by your:", cex=0.75),
       xlab= list("Percentage", cex = 0.75))

```



## Under/over age 60 on Q61

### Under/over age 60 on Q61.a (Neighbouring farmers)

```{r, echo = FALSE, fig.height = 3.5}
sgbar.likert <- prop.table(table(data$n151,data$q61a),1)*100

likert(sgbar.likert,
       main=list(label="How much is your ownership of machinery appreciated by your neighbouring farmers", cex=0.75),
       xlab= list("Percentage", cex = 0.75),
       cex.main = 2)
```

### Under/over age 60 on Q61.b (household members)

```{r, echo = FALSE, fig.height = 3.5}
sgbar.likert <- prop.table(table(data$n151,data$q61b),1)*100

likert(sgbar.likert,
       main=list(label="How much is your ownership of machinery appreciated by your household members", cex=0.75),
       xlab= list("Percentage", cex = 0.75),
       cex.main = 2)
```

## Regional variation on Q61

### Regional variation on Q61.a (Neighbouring farmers)

```{r, echo = FALSE, fig.height = 3.5}
sgbar.likert <- prop.table(table(data$id1,data$q61a),1)*100

likert(sgbar.likert,
       main=list(label="How much is your ownership of machinery appreciated by your neighbouring farmers", cex=0.75),
       xlab= list("Percentage", cex = 0.75),
       cex.main = 2)
```

### Regional variation on Q61.b (household members)

```{r, echo = FALSE, fig.height = 3.5}
sgbar.likert <- prop.table(table(data$id1,data$q61b),1)*100

likert(sgbar.likert,
       main=list(label="How much is your ownership of machinery appreciated by your household members", cex=0.75),
       xlab= list("Percentage", cex = 0.75),
       cex.main = 2)
```