---
title: "Myanmanr Farming Survey - MODULE 1 - Second Cut"
tables: yes
output:
  word_document:
    toc: yes
  html_document:
    css: custom.css
    toc: yes
---


```{r setup, echo = FALSE, warning = FALSE, message = FALSE}
library(dplyr)
library(xtable)
library(knitr)
library(RColorBrewer)
library(memisc)
load("../data/survey.data02.RData")


## merge together three tables - age, region and land ownership.
## also drop categories that don't have any cases 
FunR02Table <- function(var) {
  x <-  cbind(table(var ,data$n151 ),
              table(var ,data$n152 ),
              table(var ,data$n153 ))
  row_sub = apply(x, 1, function(row) !all(row == 0 ))
  x <- x[row_sub,]
  prop.table(x, 2)*100
}

y <-  c(table(data$n151 ),
            table(data$n152 ),
            table(data$n153 ))

Fun02Barplot <- function(var) {
  par(mar = c(10,2,1,1), xpd = TRUE)
  barplot(FunR02Table(var), width = y, space = c(.5,.5,1,.5,1,.5,.5),
        col = colorRampPalette(brewer.pal(11, "Spectral"))(nrow(FunR02Table(var))),
        legend.text = rownames(FunR02Table(var)), args.legend = list(y = -15))
}

Fun02PrintTab<- function(var){
  kable(FunR02Table(var), digits = 2, booktabs = TRUE, padding = 10)
}



FunR02TableInt<- function(var){
  data %>% 
    group_by(n151) %>%
    summarise_each(funs(min, mean, max), get(var)) %>%
    dplyr::rename( var = n151 ) -> x1
  
  data %>% 
    group_by(n152) %>%
    summarise_each(funs(min, mean, max), get(var)) %>%
    dplyr::rename( var = n152 ) -> x2
  
  data %>% 
    group_by(n153) %>%
    summarise_each(funs(min, mean, max), get(var)) %>%
    dplyr::rename( var = n153 ) -> x3
  
  tab <- t(rbind(x1,x2,x3)[2:4])
  colnames(tab) <- names(y)
  tab
}

Fun02PrintTabInt<- function(var){
  kable(FunR02TableInt(var), digits = 2, booktabs = TRUE, padding = 10)
}

Fun02BarplotInt <- function(var) {
  par(mar = c(5,2,1,1), xpd = TRUE)
  par(mfrow = c(1,3))
  boxplot(get(var) ~ n151, data)
  boxplot(get(var) ~ n152, data)
  boxplot(get(var) ~ n153, data)
  par(mfrow = c(1,1))
}

```

# Gender-Age-Education-Civil-Status-Health


## `r description(I(dataset$q1))` 

[N = `r sum(!is.na(data$q1))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q1
Fun02PrintTab(var)
Fun02Barplot(var)

```


## `r description(I(dataset$n154))`

[N = `r sum(!is.na(data$n154))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n154
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q3))`

[N = `r sum(!is.na(data$q3))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q3
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q4))`

[N = `r sum(!is.na(data$q4))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q4
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q5))`

[N = `r sum(!is.na(data$q5))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q5
Fun02PrintTab(var)
Fun02Barplot(var)
```



## `r description(I(dataset$q6_a))`
[N = `r sum(!is.na(data$q6_a))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q6_a
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q6_b))`
[N = `r sum(!is.na(data$q6_b))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q6_b
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q6_c))`
[N = `r sum(!is.na(data$q6_c))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q6_c
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q6_d))`
[N = `r sum(!is.na(data$q6_d))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q6_d
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q6_e))`
[N = `r sum(!is.na(data$q6_e))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q6_e
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q6_f))`
[N = `r sum(!is.na(data$q6_f))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q6_f
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q6_g))`
[N = `r sum(!is.na(data$q6_g))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q6_g
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q6_h))`
[N = `r sum(!is.na(data$q6_h))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q6_h
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n1))`
[N = `r sum(!is.na(data$n1))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n1
Fun02PrintTab(var)
Fun02Barplot(var)
```


# Households

## `r description(I(dataset$n155))`
[N = `r sum(!is.na(data$n155))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n155
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n160))`
[N = `r sum(!is.na(data$n160))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n160
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n2))`
[N = `r sum(!is.na(data$n2))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n2
Fun02PrintTab(var)
Fun02Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n2"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```

## `r description(I(dataset$n3))`
[N = `r sum(!is.na(data$n3))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n3
Fun02PrintTab(var)
Fun02Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n3"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```


## `r description(I(dataset$n4))`
[N = `r sum(!is.na(data$n4))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n4
Fun02PrintTab(var)
Fun02Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n4"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```

## `r description(I(dataset$n5))`
[N = `r sum(!is.na(data$n5))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n5
Fun02PrintTab(var)
Fun02Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n5"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```

## `r description(I(dataset$n6))`
[N = `r sum(!is.na(data$n6))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n6
Fun02PrintTab(var)
Fun02Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n6"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```

## `r description(I(dataset$n8))`**
[N = `r sum(!is.na(data$n8))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n8
Fun02PrintTab(var)
Fun02Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n8"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```

## `r description(I(dataset$n16))`**
[N = `r sum(!is.na(data$n16))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n16
Fun02PrintTab(var)
Fun02Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n16"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```

## `r description(I(dataset$n17))`**
[N = `r sum(!is.na(data$n17))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n17
Fun02PrintTab(var)
Fun02Barplot(var)
```


## `r description(I(dataset$n156))`
[N = `r sum(!is.na(data$n156))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n17
Fun02PrintTab(var)
Fun02Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n17"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```

## `r description(I(dataset$n157))`
[N = `r sum(!is.na(data$n157))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n157
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n18))`
[N = `r sum(!is.na(data$n18))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n18
Fun02PrintTab(var)
Fun02Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n18"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```

## `r description(I(dataset$n19))`
[N = `r sum(!is.na(data$n19))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n19
Fun02PrintTab(var)
Fun02Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n19"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```

## `r description(I(dataset$n20))`
[N = `r sum(!is.na(data$n20))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n20
Fun02PrintTab(var)
Fun02Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n20"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```

## `r description(I(dataset$n21))`
[N = `r sum(!is.na(data$n21))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n21
Fun02PrintTab(var)
Fun02Barplot(var)
```


## `r description(I(dataset$n23))`
[N = `r sum(!is.na(data$n23))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n23
Fun02PrintTab(var)
Fun02Barplot(var)
```



## `r description(I(dataset$n158))`
[N = `r sum(!is.na(data$n158))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n158
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n159))`
[N = `r sum(!is.na(data$n159))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n159
Fun02PrintTab(var)
Fun02Barplot(var)
```



## `r description(I(dataset$n24))`
[N = `r sum(!is.na(data$n24))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n24
Fun02PrintTab(var)
Fun02Barplot(var)
```


## `r description(I(dataset$n25))`
[N = `r sum(!is.na(data$n25))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n25
Fun02PrintTab(var)
Fun02Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n25"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```

## `r description(I(dataset$n26))`
[N = `r sum(!is.na(data$n26))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n26
Fun02PrintTab(var)
Fun02Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n26"
Fun02PrintTabInt(var)
```


## `r description(I(dataset$n27))`
[N = `r sum(!is.na(data$n27))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n27
Fun02PrintTab(var)
Fun02Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n27"
Fun02PrintTabInt(var)
```

## `r description(I(dataset$n28))`
[N = `r sum(!is.na(data$n28))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n28
Fun02PrintTab(var)
Fun02Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n28"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```

## `r description(I(dataset$n29))`
[N = `r sum(!is.na(data$n29))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n29
Fun02PrintTab(var)
Fun02Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n29"
Fun02PrintTabInt(var)
```

## number of generations.. **

#Income

## `r description(I(dataset$q9))`
[N = `r sum(!is.na(data$q9))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q9
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q10))`
[N = `r sum(!is.na(data$q10))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q10
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q11))`
[N = `r sum(!is.na(data$q11))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q11
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q12))`
[N = `r sum(!is.na(data$q12))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q12
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q13))`
[N = `r sum(!is.na(data$q13))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q13
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q14))`
[N = `r sum(!is.na(data$q14))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q14
Fun02PrintTab(var)
Fun02Barplot(var)
```


## `r description(I(dataset$q15_h))`
[N = `r sum(!is.na(data$q15_h))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q15_h
Fun02PrintTab(var)
Fun02Barplot(var)
```



## `r description(I(dataset$n30))`
[N = `r sum(!is.na(data$n30))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n30
Fun02PrintTab(var)
Fun02Barplot(var)
```
