---
title: "Myanmanr Farming Survey - MODULE 3 - Second Cut"
tables: yes
output:
  word_document:
    toc: yes
  html_document:
    css: custom.css
    toc: yes
---
  
  
```{r setup, echo = FALSE, warning = FALSE, message = FALSE}
library(dplyr)
library(xtable)
library(knitr)
library(RColorBrewer)
library(memisc)
load("../data/survey.data02.RData")


## merge together three tables - age, region and land ownership.
## also drop categories that don't have any cases 
FunR02Table <- function(var) {
  x <-  cbind(table(var ,data$n151 ),
              table(var ,data$n152 ),
              table(var ,data$n153 ))
  row_sub = apply(x, 1, function(row) !all(row == 0 ))
  x <- x[row_sub,]
  prop.table(x, 2)*100
}

y <-  c(table(data$n151 ),
        table(data$n152 ),
        table(data$n153 ))

Fun02Barplot <- function(var) {
  par(mar = c(10,2,1,1), xpd = TRUE)
  barplot(FunR02Table(var), width = y, space = c(.5,.5,1,.5,1,.5,.5),
          col = colorRampPalette(brewer.pal(11, "Spectral"))(nrow(FunR02Table(var))),
          legend.text = rownames(FunR02Table(var)), args.legend = list(y = -15))
}

Fun02PrintTab<- function(var){
  kable(FunR02Table(var), digits = 2, booktabs = TRUE, padding = 10)
}



FunR02TableInt<- function(var){
  data %>% 
    group_by(n151) %>%
    summarise_each(funs(min(., na.rm = TRUE), mean(., na.rm = TRUE), max(., na.rm = TRUE)), get(var)) %>%
    dplyr::rename( var = n151 ) -> x1
  
  data %>% 
    group_by(n152) %>%
    summarise_each(funs(min(., na.rm = TRUE), mean(., na.rm = TRUE), max(., na.rm = TRUE)), get(var)) %>%
    dplyr::rename( var = n152 ) -> x2
  
  data %>% 
    group_by(n153) %>%
    summarise_each(funs(min(., na.rm = TRUE), mean(., na.rm = TRUE), max(., na.rm = TRUE)), get(var)) %>%
    dplyr::rename( var = n153 ) -> x3
  
  tab <- t(rbind(x1,x2,x3)[2:4])
  colnames(tab) <- names(y)
  tab
}

Fun02PrintTabInt<- function(var){
  kable(FunR02TableInt(var), digits = 2, booktabs = TRUE, padding = 10)
}

Fun02BarplotInt <- function(var) {
  par(mar = c(5,2,1,1), xpd = TRUE)
  par(mfrow = c(1,3))
  boxplot(get(var) ~ n151, data)
  boxplot(get(var) ~ n152, data)
  boxplot(get(var) ~ n153, data)
  par(mfrow = c(1,1))
}

```

# Community challenges


## `r description(I(dataset$q46_a))` 
[N = `r sum(!is.na(data$q46_a))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q46_a
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q46_b))` 
[N = `r sum(!is.na(data$q46_b))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q46_b
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q46_c))` 
[N = `r sum(!is.na(data$q46_c))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q46_c
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q46_d))` 
[N = `r sum(!is.na(data$q46_d))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q46_d
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q46_e))` 
[N = `r sum(!is.na(data$q46_e))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q46_e
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q46_f))` 
[N = `r sum(!is.na(data$q46_f))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q46_f
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q46_g))` 
[N = `r sum(!is.na(data$q46_g))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q46_g
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q46_h))` 
[N = `r sum(!is.na(data$q46_h))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q46_h
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q46_i))` 
[N = `r sum(!is.na(data$q46_i))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q46_i
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q46_j))` 
[N = `r sum(!is.na(data$q46_j))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q46_j
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q46_k))` 
[N = `r sum(!is.na(data$q46_k))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q46_k
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q46_l))` 
[N = `r sum(!is.na(data$q46_l))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q46_l
Fun02PrintTab(var)
Fun02Barplot(var)
```


## `r description(I(dataset$n142))` 
[N = `r sum(!is.na(data$n142))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n142
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n143))` 
[N = `r sum(!is.na(data$n143))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n143
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n144))` 
[N = `r sum(!is.na(data$n144))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n144
Fun02PrintTab(var)
Fun02Barplot(var)
```

# Children leaving

## `r description(I(dataset$q47))` 
[N = `r sum(!is.na(data$q47))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q47
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q48))` 
[N = `r sum(!is.na(data$q48))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q48
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q49))` 
[N = `r sum(!is.na(data$q49))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q49
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q50))` 
[N = `r sum(!is.na(data$q50))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q50
Fun02PrintTab(var)
Fun02Barplot(var)
```

# Before I die

## `r description(I(dataset$q51_a))` 
[N = `r sum(!is.na(data$q51_a))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q51_a
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q51_b))` 
[N = `r sum(!is.na(data$q51_b))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q51_b
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q51_c))` 
[N = `r sum(!is.na(data$q51_c))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q51_c
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n145))` 
[N = `r sum(!is.na(data$n145))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n145
Fun02PrintTab(var)
Fun02Barplot(var)
```


## `r description(I(dataset$n147))` 
[N = `r sum(!is.na(data$n147))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n147
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n148))` 
[N = `r sum(!is.na(data$n148))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n148
Fun02PrintTab(var)
Fun02Barplot(var)
```
