---
title: "Myanmanr Farming Survey - MODULE 2 - Second Cut"
tables: yes
output:
  word_document:
    toc: yes
  html_document:
    css: style.css
    toc: yes
---
  
  
```{r setup, echo = FALSE, warning = FALSE, message = FALSE}
library(dplyr)
library(xtable)
library(knitr)
library(RColorBrewer)
library(memisc)
load("../data/survey.data02.RData")


## merge together three tables - age, region and land ownership.
## also drop categories that don't have any cases 
FunR02Table <- function(var) {
  x <-  cbind(table(var ,data$n151 ),
              table(var ,data$n152 ),
              table(var ,data$n153 ))
  row_sub = apply(x, 1, function(row) !all(row == 0 ))
  x <- x[row_sub,]
  prop.table(x, 2)*100
}

y <-  c(table(data$n151 ),
        table(data$n152 ),
        table(data$n153 ))

Fun02Barplot <- function(var) {
  par(mar = c(10,2,1,1), xpd = TRUE)
  barplot(FunR02Table(var), width = y, space = c(.5,.5,1,.5,1,.5,.5),
          col = colorRampPalette(brewer.pal(11, "Spectral"))(nrow(FunR02Table(var))),
          legend.text = rownames(FunR02Table(var)), args.legend = list(y = -15))
}

Fun02PrintTab<- function(var){
  kable(FunR02Table(var), digits = 2, booktabs = TRUE, padding = 10)
}



FunR02TableInt<- function(var){
  data %>% 
    group_by(n151) %>%
    summarise_each(funs(min(., na.rm = TRUE), mean(., na.rm = TRUE), max(., na.rm = TRUE)), get(var)) %>%
    dplyr::rename( var = n151 ) -> x1
  
  data %>% 
    group_by(n152) %>%
    summarise_each(funs(min(., na.rm = TRUE), mean(., na.rm = TRUE), max(., na.rm = TRUE)), get(var)) %>%
    dplyr::rename( var = n152 ) -> x2
  
  data %>% 
    group_by(n153) %>%
    summarise_each(funs(min(., na.rm = TRUE), mean(., na.rm = TRUE), max(., na.rm = TRUE)), get(var)) %>%
    dplyr::rename( var = n153 ) -> x3
  
  tab <- t(rbind(x1,x2,x3)[2:4])
  colnames(tab) <- names(y)
  tab
}

Fun02PrintTabInt<- function(var){
  kable(FunR02TableInt(var), digits = 2, booktabs = TRUE, padding = 10)
}

Fun02BarplotInt <- function(var) {
  par(mar = c(5,2,1,1), xpd = TRUE)
  par(mfrow = c(1,3))
  boxplot(get(var) ~ n151, data)
  boxplot(get(var) ~ n152, data)
  boxplot(get(var) ~ n153, data)
  par(mfrow = c(1,1))
}

```

# Land


## `r description(I(dataset$q16))` 

[N = `r sum(!is.na(data$q16))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q16
Fun02PrintTab(var)
Fun02Barplot(var)

```

## `r description(I(dataset$q17))`
[N = `r sum(!is.na(data$q17))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- "q17"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```


## `r description(I(dataset$n153))`
[N = `r sum(!is.na(data$n153))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n153
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q18))`
[N = `r sum(!is.na(data$q18))`] 
```{r results='asis', echo=FALSE, fig.height=4}
var <- "q18"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```

## `r description(I(dataset$n31))`
[N = `r sum(!is.na(data$n31))`] 
```{r results='asis', echo=FALSE, fig.height=4}
var <- "n31"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```

## `r description(I(dataset$q19))` 
[N = `r sum(!is.na(data$q19))`] 

```{r results='asis', echo=FALSE, fig.height=4}
var <- data$q19
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q20_a))`
[N = `r sum(!is.na(data$q20_a))`] 
```{r results='asis', echo=FALSE, fig.height=4}
var <- "q20_a"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```

## `r description(I(dataset$n32))`
[N = `r sum(!is.na(data$n32))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n32"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```

## `r description(I(dataset$q21))` 
[N = `r sum(!is.na(data$q21))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q21
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q22))`
[N = `r sum(!is.na(data$q22))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "q22"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```

## `r description(I(dataset$q23))`
[N = `r sum(!is.na(data$q23))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "q23"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```


## `r description(I(dataset$n33))`
[N = `r sum(!is.na(data$n33))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n33"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```

# Management

## `r description(I(dataset$q24))` 
[N = `r sum(!is.na(data$q24))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q24
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n34))` 
[N = `r sum(!is.na(data$n34))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n34
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n35))` 
[N = `r sum(!is.na(data$n35))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n35
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n36))` (either N34 or N35) 
[N = `r sum(!is.na(data$n36))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n36
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q25))` 
[N = `r sum(!is.na(data$q25))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q25
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q26))`
[N = `r sum(!is.na(data$q26))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "q26"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```

## `r description(I(dataset$q27))` 
[N = `r sum(!is.na(data$q27))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q27
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n46))` 
[N = `r sum(!is.na(data$n46))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n46
Fun02PrintTab(var)
Fun02Barplot(var)
```

# Logistics/ Challenges

## `r description(I(dataset$q29a))`
[N = `r sum(!is.na(data$q29a))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "q29a"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```

## `r description(I(dataset$q29b))`
[N = `r sum(!is.na(data$q29b))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q29b
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n47))`
[N = `r sum(!is.na(data$n47))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n47
Fun02PrintTab(var)
Fun02Barplot(var)
```


## `r description(I(dataset$n48))`
[N = `r sum(!is.na(data$n48))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n48"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```

## `r description(I(dataset$q31))`
[N = `r sum(!is.na(data$q31))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q31
Fun02PrintTab(var)
Fun02Barplot(var)
```



## `r description(I(dataset$n51))`
[N = `r sum(!is.na(data$n51))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n51"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```


## `r description(I(dataset$n57))`
[N = `r sum(!is.na(data$n57))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n57
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q32_1_1))`
[N = `r sum(!is.na(data$q32_1_1))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q32_1_1
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n59))`
[N = `r sum(!is.na(data$n59))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n59
Fun02PrintTab(var)
Fun02Barplot(var)
```


## `r description(I(dataset$q32_2_1))`
[N = `r sum(!is.na(data$q32_2_1))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q32_2_1
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n61))`
[N = `r sum(!is.na(data$n61))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n61
Fun02PrintTab(var)
Fun02Barplot(var)
```


## `r description(I(dataset$q32_3_1))`
[N = `r sum(!is.na(data$q32_3_1))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q32_3_1
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n63))`
[N = `r sum(!is.na(data$n63))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n63
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n64))`
[N = `r sum(!is.na(data$n64))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n64
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n65))`
[N = `r sum(!is.na(data$n65))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n65
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n66))`
[N = `r sum(!is.na(data$n66))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n66
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n67))`
[N = `r sum(!is.na(data$n67))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n67
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n68))`
[N = `r sum(!is.na(data$n68))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n68
Fun02PrintTab(var)
Fun02Barplot(var)
```


## `r description(I(dataset$n69))`
[N = `r sum(!is.na(data$n69))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n69
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n70))`
[N = `r sum(!is.na(data$n70))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n70"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```


## `r description(I(dataset$n76))`
[N = `r sum(!is.na(data$n76))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n76
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n77))`
[N = `r sum(!is.na(data$n77))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n77"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```


## `r description(I(dataset$n83))`
[N = `r sum(!is.na(data$n83))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n83
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n84))`
[N = `r sum(!is.na(data$n84))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n84"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```


## `r description(I(dataset$n90))`
[N = `r sum(!is.na(data$n90))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n90
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n91))`
[N = `r sum(!is.na(data$n91))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n91"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```


## `r description(I(dataset$n97))`
[N = `r sum(!is.na(data$n97))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n97
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n98))`
[N = `r sum(!is.na(data$n98))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n98"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```


## `r description(I(dataset$n103))`
[N = `r sum(!is.na(data$n103))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n103"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```

## `r description(I(dataset$n104))`
[N = `r sum(!is.na(data$n104))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n104
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n105))`
[N = `r sum(!is.na(data$n105))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n105
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n106))`
[N = `r sum(!is.na(data$n106))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n106
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n107))`
[N = `r sum(!is.na(data$n107))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n107
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n108))`
[N = `r sum(!is.na(data$n108))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n108
Fun02PrintTab(var)
Fun02Barplot(var)
```



## `r description(I(dataset$n109))`
[N = `r sum(!is.na(data$n109))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n109"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```


## `r description(I(dataset$n110))`
[N = `r sum(!is.na(data$n110))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n110"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```


## `r description(I(dataset$n111))`
[N = `r sum(!is.na(data$n111))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n111"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```


## `r description(I(dataset$n112))`
[N = `r sum(!is.na(data$n112))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n112"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```


## `r description(I(dataset$n113))`
[N = `r sum(!is.na(data$n113))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n113"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```


## `r description(I(dataset$n114))`
[N = `r sum(!is.na(data$n114))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n114"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```


## `r description(I(dataset$n115))`
[N = `r sum(!is.na(data$n115))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n115"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```


## `r description(I(dataset$n116))`
[N = `r sum(!is.na(data$n116))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n116"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```


## `r description(I(dataset$n117))`
[N = `r sum(!is.na(data$n117))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n117"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```


## `r description(I(dataset$n118))`
[N = `r sum(!is.na(data$n118))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n118"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```


## `r description(I(dataset$n119))`
[N = `r sum(!is.na(data$n119))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n119"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```



## `r description(I(dataset$n120))`
[N = `r sum(!is.na(data$n120))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n120"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```


## `r description(I(dataset$n121))`
[N = `r sum(!is.na(data$n121))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n121"
Fun02PrintTabInt(var)
Fun02BarplotInt(var) 
```


# Old Habits

## `r description(I(dataset$q37_a))`
[N = `r sum(!is.na(data$q37_a))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q37_a
Fun02PrintTab(var)
Fun02Barplot(var)
```


## `r description(I(dataset$q37_b))`
[N = `r sum(!is.na(data$q37_b))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q37_b
Fun02PrintTab(var)
Fun02Barplot(var)
```


## `r description(I(dataset$q37_c))`
[N = `r sum(!is.na(data$q37_c))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q37_c
Fun02PrintTab(var)
Fun02Barplot(var)
```


## `r description(I(dataset$q37_d))`
[N = `r sum(!is.na(data$q37_d))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q37_d
Fun02PrintTab(var)
Fun02Barplot(var)
```


## `r description(I(dataset$q37_e))`
[N = `r sum(!is.na(data$q37_e))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q37_e
Fun02PrintTab(var)
Fun02Barplot(var)
```


## `r description(I(dataset$q37_f))`
[N = `r sum(!is.na(data$q37_f))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q37_f
Fun02PrintTab(var)
Fun02Barplot(var)
```


## `r description(I(dataset$q37_g))`
[N = `r sum(!is.na(data$q37_g))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q37_g
Fun02PrintTab(var)
Fun02Barplot(var)
```


## `r description(I(dataset$q37_h))`
[N = `r sum(!is.na(data$q37_h))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q37_h
Fun02PrintTab(var)
Fun02Barplot(var)
```


## `r description(I(dataset$q37_i))`
[N = `r sum(!is.na(data$q37_i))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q37_i
Fun02PrintTab(var)
Fun02Barplot(var)
```


## `r description(I(dataset$q37_j))`
[N = `r sum(!is.na(data$q37_j))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q37_j
Fun02PrintTab(var)
Fun02Barplot(var)
```


## `r description(I(dataset$n122))`
[N = `r sum(!is.na(data$n122))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n122
Fun02PrintTab(var)
Fun02Barplot(var)
```



## `r description(I(dataset$q38))`
[N = `r sum(!is.na(data$q38))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q38
Fun02PrintTab(var)
Fun02Barplot(var)
```


## `r description(I(dataset$n123))`
[N = `r sum(!is.na(data$n123))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n123
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n124))`
[N = `r sum(!is.na(data$n124))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n124
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n125))`
[N = `r sum(!is.na(data$n125))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n125
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n126))`
[N = `r sum(!is.na(data$n126))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n126
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n127))`
[N = `r sum(!is.na(data$n127))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n127
Fun02PrintTab(var)
Fun02Barplot(var)
```


## `r description(I(dataset$n128))`
[N = `r sum(!is.na(data$n128))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n128
Fun02PrintTab(var)
Fun02Barplot(var)
```


## `r description(I(dataset$n129))`
[N = `r sum(!is.na(data$n129))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n129
Fun02PrintTab(var)
Fun02Barplot(var)
```


## `r description(I(dataset$n130))`
[N = `r sum(!is.na(data$n130))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n130
Fun02PrintTab(var)
Fun02Barplot(var)
```


## `r description(I(dataset$n131))`
[N = `r sum(!is.na(data$n131))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n131
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n133))`
[N = `r sum(!is.na(data$n133))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n133
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n134))`
[N = `r sum(!is.na(data$n134))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n134
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n135))`
[N = `r sum(!is.na(data$n135))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n135
Fun02PrintTab(var)
Fun02Barplot(var)
```


## `r description(I(dataset$q41))`
[N = `r sum(!is.na(data$q41))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q41
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q42))`
[N = `r sum(!is.na(data$q42))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q42
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n136))`
[N = `r sum(!is.na(data$n136))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n136
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n137))`
[N = `r sum(!is.na(data$n137))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n137
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n138))`
[N = `r sum(!is.na(data$n138))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n138
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n139))`
[N = `r sum(!is.na(data$n139))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n139
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q45_a))`
[N = `r sum(!is.na(data$q45_a))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q45_a
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q45_b))`
[N = `r sum(!is.na(data$q45_b))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q45_b
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q45_c))`
[N = `r sum(!is.na(data$q45_c))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q45_c
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q45_d))`
[N = `r sum(!is.na(data$q45_d))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q45_d
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q45_e))`
[N = `r sum(!is.na(data$q45_e))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q45_e
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q45_f))`
[N = `r sum(!is.na(data$q45_f))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q45_f
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q45_g))`
[N = `r sum(!is.na(data$q45_g))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q45_g
Fun02PrintTab(var)
Fun02Barplot(var)
```


## `r description(I(dataset$q45_h))`
[N = `r sum(!is.na(data$q45_h))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q45_h
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q45_i))`
[N = `r sum(!is.na(data$q45_i))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q45_i
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q45_j))`
[N = `r sum(!is.na(data$q45_j))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q45_j
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q45_k))`
[N = `r sum(!is.na(data$q45_k))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q45_k
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q45_l))`
[N = `r sum(!is.na(data$q45_l))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q45_l
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q45_m))`
[N = `r sum(!is.na(data$q45_m))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q45_m
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$q45_n))`
[N = `r sum(!is.na(data$q45_n))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q45_n
Fun02PrintTab(var)
Fun02Barplot(var)
```

## `r description(I(dataset$n140))`
[N = `r sum(!is.na(data$n140))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n140
Fun02PrintTab(var)
Fun02Barplot(var)
```


## `r description(I(dataset$n141))`
[N = `r sum(!is.na(data$n141))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n141
Fun02PrintTab(var)
Fun02Barplot(var)
```

