---
title: "Myanmanr Farming Survey - MODULE 4 - Third Cut"
tables: yes
output:
  html_document:
    css: custom.css
    toc: yes
  word_document:
    toc: yes
---
  


```{r setup, echo = FALSE, warning = FALSE, message = FALSE}
source("R03-MyFunctions.R")
```


# Resources

## `r description(I(dataset$q53_a))` 
[N = `r sum(!is.na(data$q53_a))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q53_a
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$q53_b))` 
[N = `r sum(!is.na(data$q53_b))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q53_b
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n161))`
[N = `r sum(!is.na(data$n161))`] 
```{r results='asis', echo=FALSE, fig.height=4}
var <- "n161"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```



## `r description(I(dataset$q54_a))` 
[N = `r sum(!is.na(data$q54_a))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q54_a
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$n162))` 
[N = `r sum(!is.na(data$n162))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n162
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$n163))`
[N = `r sum(!is.na(data$n163))`] 
```{r results='asis', echo=FALSE, fig.height=4}
var <- "n163"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```

## `r description(I(dataset$n164))` 
[N = `r sum(!is.na(data$n164))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n164
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n165))`
[N = `r sum(!is.na(data$n165))`] 
```{r results='asis', echo=FALSE, fig.height=4}
var <- "n165"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```

## `r description(I(dataset$n166))` 
[N = `r sum(!is.na(data$n166))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n166
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n167))`
[N = `r sum(!is.na(data$n167))`] 
```{r results='asis', echo=FALSE, fig.height=4}
var <- "n167"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```

## `r description(I(dataset$n168))` 
[N = `r sum(!is.na(data$n168))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n168
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n169))`
[N = `r sum(!is.na(data$n169))`] 
```{r results='asis', echo=FALSE, fig.height=4}
var <- "n169"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```


## `r description(I(dataset$n170))` 
[N = `r sum(!is.na(data$n170))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n170
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n171))`
[N = `r sum(!is.na(data$n171))`] 
```{r results='asis', echo=FALSE, fig.height=4}
var <- "n171"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```


## `r description(I(dataset$n172))` 
[N = `r sum(!is.na(data$n172))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n172
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n173))`
[N = `r sum(!is.na(data$n173))`] 
```{r results='asis', echo=FALSE, fig.height=4}
var <- "n173"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```


## `r description(I(dataset$n174))` 
[N = `r sum(!is.na(data$n174))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n174
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n175))`
[N = `r sum(!is.na(data$n175))`] 
```{r results='asis', echo=FALSE, fig.height=4}
var <- "n175"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```


## `r description(I(dataset$n176))`
[N = `r sum(!is.na(data$n176))`] 
```{r results='asis', echo=FALSE, fig.height=4}
var <- "n176"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```

# Plans

## `r description(I(dataset$q55))` 
[N = `r sum(!is.na(data$q55))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q55
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$q56_a))` 
[N = `r sum(!is.na(data$q56_a))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q56_a
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q56_b))` 
[N = `r sum(!is.na(data$q56_b))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q56_b
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q56_c))` 
[N = `r sum(!is.na(data$q56_c))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q56_c
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```
## `r description(I(dataset$q56_d))` 
[N = `r sum(!is.na(data$q56_d))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q56_d
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```
## `r description(I(dataset$q56_e))` 
[N = `r sum(!is.na(data$q56_e))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q56_e
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```
## `r description(I(dataset$q56_f))` 
[N = `r sum(!is.na(data$q56_f))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q56_f
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n150))` 
[N = `r sum(!is.na(data$n150))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n150
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$q57a))` 
[N = `r sum(!is.na(data$q57a))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q57a)
```


## `r description(I(dataset$q57b))` 
[N = `r sum(!is.na(data$q57b))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q57b)
```

## `r description(I(dataset$q57c))` 
[N = `r sum(!is.na(data$q57c))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q57c)
```


## `r description(I(dataset$q57d))` 
[N = `r sum(!is.na(data$q57d))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q57d)
```


## `r description(I(dataset$q58a))` 
[N = `r sum(!is.na(data$q58a))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q58a)
```


## `r description(I(dataset$q58b))` 
[N = `r sum(!is.na(data$q58b))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q58b)
```


## `r description(I(dataset$q58c))` 
[N = `r sum(!is.na(data$q58c))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q58c)
```


## `r description(I(dataset$q58d))` 
[N = `r sum(!is.na(data$q58d))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q58d)
```


## `r description(I(dataset$q59a))` 
[N = `r sum(!is.na(data$q59a))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q59a)
```


## `r description(I(dataset$q59b))` 
[N = `r sum(!is.na(data$q59b))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q59b)
```


## `r description(I(dataset$q59c))` 
[N = `r sum(!is.na(data$q59c))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q59c)
```


## `r description(I(dataset$q59d))` 
[N = `r sum(!is.na(data$q59d))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q59d)
```


## `r description(I(dataset$q59e))` 
[N = `r sum(!is.na(data$q59e))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q59e)
```


## `r description(I(dataset$q60a))` 
[N = `r sum(!is.na(data$q60a))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q60a)
```



## `r description(I(dataset$q60b))` 
[N = `r sum(!is.na(data$q60b))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q60b)
```



## `r description(I(dataset$q60c))` 
[N = `r sum(!is.na(data$q60c))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q60c)
```


## `r description(I(dataset$q60d))` 
[N = `r sum(!is.na(data$q60d))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q60d)
```



## `r description(I(dataset$q60e))` 
[N = `r sum(!is.na(data$q60e))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q60e)
```



## `r description(I(dataset$q61a))` 
[N = `r sum(!is.na(data$q61a))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q61a)
```



## `r description(I(dataset$q61b))` 
[N = `r sum(!is.na(data$q61b))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q61b)
```


## `r description(I(dataset$q62a))` 
[N = `r sum(!is.na(data$q62a))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q62a)
```


## `r description(I(dataset$q62b))` 
[N = `r sum(!is.na(data$q62b))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q62b)
```
 
# Pesticides

## `r description(I(dataset$module_4_2))` 
[N = `r sum(!is.na(data$module_4_2))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$module_4_2
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q64_a))` 
[N = `r sum(!is.na(data$q64_a))`] 
```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q64_a)
```


## `r description(I(dataset$q64_b))` 
[N = `r sum(!is.na(data$q64_b))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q64_b)
```
```

## `r description(I(dataset$q64_c))` 
[N = `r sum(!is.na(data$q64_c))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q64_c)
```

## `r description(I(dataset$q64_d))` 
[N = `r sum(!is.na(data$q64_d))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q64_d)
```

## `r description(I(dataset$q65_a))` 
[N = `r sum(!is.na(data$q65_a))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q65_a)
```

## `r description(I(dataset$q65_b))` 
[N = `r sum(!is.na(data$q65_b))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q65_b)
```

## `r description(I(dataset$q65_c))` 
[N = `r sum(!is.na(data$q65_c))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q65_c)
```

## `r description(I(dataset$q65_d))` 
[N = `r sum(!is.na(data$q65_d))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q65_d)
```

## `r description(I(dataset$q66_a))` 
[N = `r sum(!is.na(data$q66_a))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q66_a)
```

## `r description(I(dataset$q66_b))` 
[N = `r sum(!is.na(data$q66_b))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q66_b)
```

## `r description(I(dataset$q66_c))` 
[N = `r sum(!is.na(data$q66_c))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q66_c)
```

## `r description(I(dataset$q66_d))` 
[N = `r sum(!is.na(data$q66_d))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q66_d)
```

## `r description(I(dataset$q67_a))` 
[N = `r sum(!is.na(data$q67_a))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q67_a)
```

## `r description(I(dataset$q67_b))` 
[N = `r sum(!is.na(data$q67_b))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q67_b)
```

## `r description(I(dataset$q67_c))` 
[N = `r sum(!is.na(data$q67_c))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q67_c)
```

## `r description(I(dataset$q67_d))` 
[N = `r sum(!is.na(data$q67_d))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q67_d)
```

## `r description(I(dataset$q68))` 
[N = `r sum(!is.na(data$q68))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q68)
```

## `r description(I(dataset$q69))` 
[N = `r sum(!is.na(data$q69))`] 

```{r, echo = FALSE, fig.height = 6}
Fun03Likert(data$q69)
```
