---
title: "Myanmanr Farming Survey - MODULE 1 - Third Cut"
tables: yes
output:
  html_document:
    css: custom.css
    toc: yes
  word_document:
    toc: yes
---
  
  
```{r setup, echo = FALSE, warning = FALSE, message = FALSE}
library(dplyr)
library(tidyr)
library(xtable)
library(knitr)
library(RColorBrewer)
library(memisc)
load("../data/survey.data02.RData")

## FUN1 categorical variables
###############################################################################
## TABLES

FunR03Table <- function(var) {
  var %>% table(Var = ., Age.group = data$n151 , Region = data$n152) %>% 
    prop.table(c(2,3)) 
  }

Fun03PrintTab <- function(var) {
  tabz <- FunR03Table(var)
  cbind(`Dry zone - 60 or over (%)` = tabz[,1,1], 
        `Dry zone - under 60 (%)` = tabz[,2,1],
        `Delta zone - 60 or over (%)` = tabz[,1,2], 
        `Delta zone - under 60 (%)` = tabz[,2,2],
        `Total sample (%)` = prop.table(table(var))) -> tab.print
  # remove row where there are no cases (otherwise a few errors..)
  row_sub = apply(tab.print, 1, function(row) !all(row == 0 ))
  tab.print <- tab.print[row_sub,]
  return(list(kable(tab.print, digits = 2, booktabs = TRUE, padding = 10),
         rownames(tab.print)))
}

y <-  c(table(data$n151, data$n152))

Fun03Barplot <- function(var) {
  par(mfrow = c(2,1), xpd = TRUE)
  par(mar = c(3,2,1,9))
  barplot(FunR03Table(var)[,,1], horiz = TRUE, 
          main = "Dry zone",
          col = colorRampPalette(brewer.pal(11, "Spectral"))(nrow(FunR03Table(var))),
          legend.text = Fun03PrintTab(var)[[2]], args.legend = list( x = 1.01,y = 300, xjust = 0),
          width = y[1:2])
  barplot(FunR03Table(var)[,,2], horiz = TRUE,
          main = "Delta",
          col = colorRampPalette(brewer.pal(11, "Spectral"))(nrow(FunR03Table(var))),
          width = y[3:4])
}


## interval variables
###############################################################################

FunR03TableInt <- function(var) {
  data %>%
    group_by(n152, n151) %>%
    summarise_each(funs(min, mean, max), get(var)) %>%
    unite(gr, n152, n151, sep = " - ") -> x1
  tab <- t(x1[2:4])
  tab <- cbind(tab, t(summarise_each(data, funs(min, mean, max), get(var))))
  colnames(tab) <- c(x1[[1]], "Total")
  tab
}

Fun03PrintTabInt<- function(var){
  kable(FunR03TableInt(var), digits = 2, booktabs = TRUE, padding = 10)
}




Fun03BarplotInt <- function(var) {
  par(mar = c(5,1.5,1,.1), xpd = TRUE)
  boxplot(get(var) ~ n151 + n152, data, cex.axis= 0.6)
  par(mfrow = c(1,1))
}


```




# Gender-Age-Education-Civil-Status-Health


## `r description(I(dataset$q1))` 

[N = `r sum(!is.na(data$q1))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q1
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)

```


## `r description(I(dataset$n154))`

[N = `r sum(!is.na(data$n154))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n154
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q3))`

[N = `r sum(!is.na(data$q3))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q3
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q4))`

[N = `r sum(!is.na(data$q4))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q4
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q5))`

[N = `r sum(!is.na(data$q5))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q5
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```



## `r description(I(dataset$q6_a))`
[N = `r sum(!is.na(data$q6_a))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q6_a
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q6_b))`
[N = `r sum(!is.na(data$q6_b))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q6_b
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q6_c))`
[N = `r sum(!is.na(data$q6_c))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q6_c
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q6_d))`
[N = `r sum(!is.na(data$q6_d))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q6_d
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q6_e))`
[N = `r sum(!is.na(data$q6_e))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q6_e
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q6_f))`
[N = `r sum(!is.na(data$q6_f))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q6_f
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q6_g))`
[N = `r sum(!is.na(data$q6_g))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q6_g
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q6_h))`
[N = `r sum(!is.na(data$q6_h))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q6_h
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n1))`
[N = `r sum(!is.na(data$n1))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n1
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


# Households

## `r description(I(dataset$n155))`
[N = `r sum(!is.na(data$n155))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n155
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n160))`
[N = `r sum(!is.na(data$n160))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n160
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n2))`
[N = `r sum(!is.na(data$n2))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n2
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n2"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```

## `r description(I(dataset$n3))`
[N = `r sum(!is.na(data$n3))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n3
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n3"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```


## `r description(I(dataset$n4))`
[N = `r sum(!is.na(data$n4))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n4
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n4"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```

## `r description(I(dataset$n5))`
[N = `r sum(!is.na(data$n5))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n5
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n5"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```

## `r description(I(dataset$n6))`
[N = `r sum(!is.na(data$n6))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n6
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n6"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```

## `r description(I(dataset$n8))`**
[N = `r sum(!is.na(data$n8))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n8
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n8"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```

## `r description(I(dataset$n16))`**
[N = `r sum(!is.na(data$n16))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n16
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n16"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```

## `r description(I(dataset$n17))`**
[N = `r sum(!is.na(data$n17))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n17
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$n156))`
[N = `r sum(!is.na(data$n156))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n17
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n17"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```

## `r description(I(dataset$n157))`
[N = `r sum(!is.na(data$n157))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n157
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n18))`
[N = `r sum(!is.na(data$n18))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n18
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n18"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```

## `r description(I(dataset$n19))`
[N = `r sum(!is.na(data$n19))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n19
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n19"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```

## `r description(I(dataset$n20))`
[N = `r sum(!is.na(data$n20))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n20
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n20"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```

## `r description(I(dataset$n21))`
[N = `r sum(!is.na(data$n21))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n21
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$n23))`
[N = `r sum(!is.na(data$n23))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n23
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```



## `r description(I(dataset$n158))`
[N = `r sum(!is.na(data$n158))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n158
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n159))`
[N = `r sum(!is.na(data$n159))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n159
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```



## `r description(I(dataset$n24))`
[N = `r sum(!is.na(data$n24))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n24
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$n25))`
[N = `r sum(!is.na(data$n25))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n25
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n25"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```

## `r description(I(dataset$n26))`
[N = `r sum(!is.na(data$n26))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n26
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n26"
Fun03PrintTabInt(var)
```


## `r description(I(dataset$n27))`
[N = `r sum(!is.na(data$n27))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n27
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n27"
Fun03PrintTabInt(var)
```

## `r description(I(dataset$n28))`
[N = `r sum(!is.na(data$n28))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n28
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n28"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```

## `r description(I(dataset$n29))`
[N = `r sum(!is.na(data$n29))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n29
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n29"
Fun03PrintTabInt(var)
```

## number of generations.. **

#Income

## `r description(I(dataset$q9))`
[N = `r sum(!is.na(data$q9))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q9
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q10))`
[N = `r sum(!is.na(data$q10))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q10
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q11))`
[N = `r sum(!is.na(data$q11))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q11
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q12))`
[N = `r sum(!is.na(data$q12))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q12
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q13))`
[N = `r sum(!is.na(data$q13))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q13
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q14))`
[N = `r sum(!is.na(data$q14))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q14
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$q15_h))`
[N = `r sum(!is.na(data$q15_h))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q15_h
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```



## `r description(I(dataset$n30))`
[N = `r sum(!is.na(data$n30))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n30
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```
