---
title: "Myanmanr Farming Survey - MODULE 3 - Third Cut"
tables: yes
output:
  word_document:
    toc: yes
  html_document:
    css: custom.css
    toc: yes
---
  
```{r setup, echo = FALSE, warning = FALSE, message = FALSE}
source("R03-MyFunctions.R")
```

# Community challenges


## `r description(I(dataset$q46_a))` 
[N = `r sum(!is.na(data$q46_a))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q46_a
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q46_b))` 
[N = `r sum(!is.na(data$q46_b))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q46_b
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q46_c))` 
[N = `r sum(!is.na(data$q46_c))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q46_c
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q46_d))` 
[N = `r sum(!is.na(data$q46_d))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q46_d
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q46_e))` 
[N = `r sum(!is.na(data$q46_e))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q46_e
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q46_f))` 
[N = `r sum(!is.na(data$q46_f))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q46_f
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q46_g))` 
[N = `r sum(!is.na(data$q46_g))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q46_g
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q46_h))` 
[N = `r sum(!is.na(data$q46_h))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q46_h
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q46_i))` 
[N = `r sum(!is.na(data$q46_i))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q46_i
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q46_j))` 
[N = `r sum(!is.na(data$q46_j))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q46_j
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q46_k))` 
[N = `r sum(!is.na(data$q46_k))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q46_k
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q46_l))` 
[N = `r sum(!is.na(data$q46_l))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q46_l
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$n142))` 
[N = `r sum(!is.na(data$n142))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n142
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n143))` 
[N = `r sum(!is.na(data$n143))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n143
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n144))` 
[N = `r sum(!is.na(data$n144))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n144
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

# Children leaving

## `r description(I(dataset$q47))` 
[N = `r sum(!is.na(data$q47))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q47
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q48))` 
[N = `r sum(!is.na(data$q48))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q48
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q49))` 
[N = `r sum(!is.na(data$q49))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q49
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q50))` 
[N = `r sum(!is.na(data$q50))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q50
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

# Before I die

## `r description(I(dataset$q51_a))` 
[N = `r sum(!is.na(data$q51_a))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q51_a
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q51_b))` 
[N = `r sum(!is.na(data$q51_b))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q51_b
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q51_c))` 
[N = `r sum(!is.na(data$q51_c))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q51_c
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n145))` 
[N = `r sum(!is.na(data$n145))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n145
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$n147))` 
[N = `r sum(!is.na(data$n147))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n147
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n148))` 
[N = `r sum(!is.na(data$n148))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n148
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```
