---
title: "Myanmanr Farming Survey - MODULE 2 - Third Cut"
tables: yes
output:
  word_document:
    toc: yes
  html_document:
    css: custom.css
    toc: yes
---
  
  
```{r setup, echo = FALSE, warning = FALSE, message = FALSE}
source("R03-MyFunctions.R")
```

# Land


## `r description(I(dataset$q16))` 

[N = `r sum(!is.na(data$q16))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q16
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)

```

## `r description(I(dataset$q17))`
[N = `r sum(!is.na(data$q17))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- "q17"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```


## `r description(I(dataset$n153))`
[N = `r sum(!is.na(data$n153))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n153
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q18))`
[N = `r sum(!is.na(data$q18))`] 
```{r results='asis', echo=FALSE, fig.height=4}
var <- "q18"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```

## `r description(I(dataset$n31))`
[N = `r sum(!is.na(data$n31))`] 
```{r results='asis', echo=FALSE, fig.height=4}
var <- "n31"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```

## `r description(I(dataset$q19))` 
[N = `r sum(!is.na(data$q19))`] 

```{r results='asis', echo=FALSE, fig.height=4}
var <- data$q19
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q20_a))`
[N = `r sum(!is.na(data$q20_a))`] 
```{r results='asis', echo=FALSE, fig.height=4}
var <- "q20_a"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```

## `r description(I(dataset$n32))`
[N = `r sum(!is.na(data$n32))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n32"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```

## `r description(I(dataset$q21))` 
[N = `r sum(!is.na(data$q21))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q21
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q22))`
[N = `r sum(!is.na(data$q22))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "q22"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```

## `r description(I(dataset$q23))`
[N = `r sum(!is.na(data$q23))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "q23"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```


## `r description(I(dataset$n33))`
[N = `r sum(!is.na(data$n33))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n33"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```

# Management

## `r description(I(dataset$q24))` 
[N = `r sum(!is.na(data$q24))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q24
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n34))` 
[N = `r sum(!is.na(data$n34))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n34
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n35))` 
[N = `r sum(!is.na(data$n35))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n35
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n36))` (either N34 or N35) 
[N = `r sum(!is.na(data$n36))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n36
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q25))` 
[N = `r sum(!is.na(data$q25))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q25
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q26))`
[N = `r sum(!is.na(data$q26))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "q26"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```

## `r description(I(dataset$q27))` 
[N = `r sum(!is.na(data$q27))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q27
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n46))` 
[N = `r sum(!is.na(data$n46))`] 

```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n46
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

# Logistics/ Challenges

## `r description(I(dataset$q29a))`
[N = `r sum(!is.na(data$q29a))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "q29a"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```

## `r description(I(dataset$q29b))`
[N = `r sum(!is.na(data$q29b))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q29b
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n47))`
[N = `r sum(!is.na(data$n47))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n47
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$n48))`
[N = `r sum(!is.na(data$n48))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n48"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```

## `r description(I(dataset$q31))`
[N = `r sum(!is.na(data$q31))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q31
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```



## `r description(I(dataset$n51))`
[N = `r sum(!is.na(data$n51))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n51"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```


## `r description(I(dataset$n57))`
[N = `r sum(!is.na(data$n57))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n57
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q32_1_1))`
[N = `r sum(!is.na(data$q32_1_1))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q32_1_1
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n59))`
[N = `r sum(!is.na(data$n59))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n59
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$q32_2_1))`
[N = `r sum(!is.na(data$q32_2_1))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q32_2_1
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n61))`
[N = `r sum(!is.na(data$n61))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n61
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$q32_3_1))`
[N = `r sum(!is.na(data$q32_3_1))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q32_3_1
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n63))`
[N = `r sum(!is.na(data$n63))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n63
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n64))`
[N = `r sum(!is.na(data$n64))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n64
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n65))`
[N = `r sum(!is.na(data$n65))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n65
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n66))`
[N = `r sum(!is.na(data$n66))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n66
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n67))`
[N = `r sum(!is.na(data$n67))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n67
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n68))`
[N = `r sum(!is.na(data$n68))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n68
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$n69))`
[N = `r sum(!is.na(data$n69))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n69
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n70))`
[N = `r sum(!is.na(data$n70))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n70"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```


## `r description(I(dataset$n76))`
[N = `r sum(!is.na(data$n76))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n76
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n77))`
[N = `r sum(!is.na(data$n77))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n77"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```


## `r description(I(dataset$n83))`
[N = `r sum(!is.na(data$n83))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n83
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n84))`
[N = `r sum(!is.na(data$n84))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n84"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```


## `r description(I(dataset$n90))`
[N = `r sum(!is.na(data$n90))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n90
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n91))`
[N = `r sum(!is.na(data$n91))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n91"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```


## `r description(I(dataset$n97))`
[N = `r sum(!is.na(data$n97))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n97
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n98))`
[N = `r sum(!is.na(data$n98))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n98"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```


## `r description(I(dataset$n103))`
[N = `r sum(!is.na(data$n103))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n103"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```

## `r description(I(dataset$n104))`
[N = `r sum(!is.na(data$n104))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n104
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n105))`
[N = `r sum(!is.na(data$n105))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n105
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n106))`
[N = `r sum(!is.na(data$n106))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n106
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n107))`
[N = `r sum(!is.na(data$n107))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n107
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n108))`
[N = `r sum(!is.na(data$n108))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n108
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```



## `r description(I(dataset$n109))`
[N = `r sum(!is.na(data$n109))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n109"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```


## `r description(I(dataset$n110))`
[N = `r sum(!is.na(data$n110))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n110"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```


## `r description(I(dataset$n111))`
[N = `r sum(!is.na(data$n111))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n111"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```


## `r description(I(dataset$n112))`
[N = `r sum(!is.na(data$n112))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n112"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```


## `r description(I(dataset$n113))`
[N = `r sum(!is.na(data$n113))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n113"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```


## `r description(I(dataset$n114))`
[N = `r sum(!is.na(data$n114))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n114"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```


## `r description(I(dataset$n115))`
[N = `r sum(!is.na(data$n115))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n115"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```


## `r description(I(dataset$n116))`
[N = `r sum(!is.na(data$n116))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n116"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```


## `r description(I(dataset$n117))`
[N = `r sum(!is.na(data$n117))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n117"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```


## `r description(I(dataset$n118))`
[N = `r sum(!is.na(data$n118))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n118"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```


## `r description(I(dataset$n119))`
[N = `r sum(!is.na(data$n119))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n119"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```



## `r description(I(dataset$n120))`
[N = `r sum(!is.na(data$n120))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n120"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```


## `r description(I(dataset$n121))`
[N = `r sum(!is.na(data$n121))`] 
```{r results='asis', echo=FALSE, fig.height=3}
var <- "n121"
Fun03PrintTabInt(var)
Fun03BarplotInt(var) 
```


# Old Habits

## `r description(I(dataset$q37_a))`
[N = `r sum(!is.na(data$q37_a))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q37_a
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$q37_b))`
[N = `r sum(!is.na(data$q37_b))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q37_b
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$q37_c))`
[N = `r sum(!is.na(data$q37_c))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q37_c
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$q37_d))`
[N = `r sum(!is.na(data$q37_d))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q37_d
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$q37_e))`
[N = `r sum(!is.na(data$q37_e))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q37_e
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$q37_f))`
[N = `r sum(!is.na(data$q37_f))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q37_f
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$q37_g))`
[N = `r sum(!is.na(data$q37_g))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q37_g
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$q37_h))`
[N = `r sum(!is.na(data$q37_h))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q37_h
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$q37_i))`
[N = `r sum(!is.na(data$q37_i))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q37_i
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$q37_j))`
[N = `r sum(!is.na(data$q37_j))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q37_j
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$n122))`
[N = `r sum(!is.na(data$n122))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n122
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```



## `r description(I(dataset$q38))`
[N = `r sum(!is.na(data$q38))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q38
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$n123))`
[N = `r sum(!is.na(data$n123))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n123
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n124))`
[N = `r sum(!is.na(data$n124))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n124
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n125))`
[N = `r sum(!is.na(data$n125))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n125
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n126))`
[N = `r sum(!is.na(data$n126))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n126
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n127))`
[N = `r sum(!is.na(data$n127))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n127
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$n128))`
[N = `r sum(!is.na(data$n128))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n128
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$n129))`
[N = `r sum(!is.na(data$n129))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n129
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$n130))`
[N = `r sum(!is.na(data$n130))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n130
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$n131))`
[N = `r sum(!is.na(data$n131))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n131
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n133))`
[N = `r sum(!is.na(data$n133))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n133
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n134))`
[N = `r sum(!is.na(data$n134))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n134
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n135))`
[N = `r sum(!is.na(data$n135))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n135
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$q41))`
[N = `r sum(!is.na(data$q41))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q41
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q42))`
[N = `r sum(!is.na(data$q42))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q42
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n136))`
[N = `r sum(!is.na(data$n136))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n136
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n137))`
[N = `r sum(!is.na(data$n137))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n137
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n138))`
[N = `r sum(!is.na(data$n138))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n138
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n139))`
[N = `r sum(!is.na(data$n139))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n139
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q45_a))`
[N = `r sum(!is.na(data$q45_a))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q45_a
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q45_b))`
[N = `r sum(!is.na(data$q45_b))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q45_b
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q45_c))`
[N = `r sum(!is.na(data$q45_c))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q45_c
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q45_d))`
[N = `r sum(!is.na(data$q45_d))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q45_d
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q45_e))`
[N = `r sum(!is.na(data$q45_e))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q45_e
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q45_f))`
[N = `r sum(!is.na(data$q45_f))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q45_f
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q45_g))`
[N = `r sum(!is.na(data$q45_g))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q45_g
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$q45_h))`
[N = `r sum(!is.na(data$q45_h))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q45_h
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q45_i))`
[N = `r sum(!is.na(data$q45_i))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q45_i
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q45_j))`
[N = `r sum(!is.na(data$q45_j))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q45_j
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q45_k))`
[N = `r sum(!is.na(data$q45_k))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q45_k
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q45_l))`
[N = `r sum(!is.na(data$q45_l))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q45_l
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q45_m))`
[N = `r sum(!is.na(data$q45_m))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q45_m
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$q45_n))`
[N = `r sum(!is.na(data$q45_n))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$q45_n
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

## `r description(I(dataset$n140))`
[N = `r sum(!is.na(data$n140))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n140
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```


## `r description(I(dataset$n141))`
[N = `r sum(!is.na(data$n141))`] 
```{r results='asis', echo=FALSE, fig.height=6}
var <- data$n141
Fun03PrintTab(var)[[1]]
Fun03Barplot(var)
```

